A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-10 Main.Rmd
微修正。

  On the other hand, in descriptive studies that make no assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
  It is better for researchers to report on the ‘general’ characteristics of the leaves in these studies.
  Therefore, the interaction should be tested so as not to make biased evaluations.
  If there is any interaction, the results should be descriptively reported and should not be generalized.
  When the measurements are made only under a single-pattern of SPD of measuring light because there is no other option, the light source must be described in the materials and methods section so that the reader knows the SPD.

>>>>

  On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
  It is better for researchers to report on the ‘general’ characteristics of the leaves in these studies.
  Therefore, the interaction should be tested so as not to make biased evaluations.
  If there is any interaction, the results should be descriptively reported and should not be generalized.
  When the measurements are made only under a single-pattern of SPD of measuring light because there is no other option, the light source must be described in the materials and methods section so that the reader knows the SPD.
